\Title

### 2022-09-14 Grimaldi-etal-BiolCybernetics.tex
Update on Overleaf.

Let us highlight some novelties of the contributions reported in this paper. First, the generic hetero-synaptic model is formalized from first
principles of optimally detecting spatio-temporal event-based signal, while []  use a heuristic based on correlation, which we have proved to be less efficient. \note{compared to HOTS~\citep{lagorce_hots_2017} the weights are explainable as they directly give the logit (inverse sigmoid of the probability) for contributing to detect each spatio-temporal spiking motif.} The model learns simultaneously the weights and delays, while the polychronization model (Izhikevich 2006) only learns weights using STDP while delays are drawn randomly and theit values frozen. Moreover, the model is evaluated on a realistic task, while models
such as the tempotron are tested on simplified problems~\citep{gutig_tempotron_2006}. Foremost, the main contribution is to bring forward a model which is adapted to spatio-temporal spiking motifs and able to be trained in a supervised manner. This allows a more flexible definition of the model using a properly labelled dataset instead of relying on a minute description of the physical rules governing a task, for instance the
luminance conservation principle for motion detection (Bensman 2012, Dardeletz).

@@

Note that this supervised learning scheme can be extended to a variety of tasks. It would follow from the emergence of new kernels adapted to this new task after supervised learning.  This constitutes a major advantage over other algorithms which derive event-based algorithms from specific physical rules (see for instance~\citep{benosman_asynchronous_2012} for computing the optic flow using the luminance conservation rule). We aim at extending the application of this model on more generic datasets acquired in natural conditions for progressively more complex tasks from motion extraction, optic flow or time-to-contact maps.
%

>>>>

Let us highlight some novelties of the contributions reported in this paper. First, the generic hetero-synaptic model is formalized from first
principles of optimally detecting spatio-temporal event-based signal, while []  use a heuristic based on correlation, which we have proved to be less efficient. \note{compared to HOTS~\citep{lagorce_hots_2017} the weights are explainable as they directly give the logit (inverse sigmoid of the probability) for contributing to detect each spatio-temporal spiking motif.} The model learns simultaneously the weights and delays, while the polychronization model (Izhikevich 2006) only learns weights using STDP while delays are drawn randomly and theit values frozen. Moreover, the model is evaluated on a realistic task, while models such as the tempotron are tested on simplified problems~\citep{gutig_tempotron_2006}. Foremost, the main contribution is to bring forward a model which is adapted to any spatio-temporal spiking motifs and able to be trained in a supervised manner by giving a dataset of supervison pairs. This allows a more flexible definition of the model using this properly labelled dataset instead of relying on a minute description of the physical rules governing a task, for instance the luminance conservation principle for motion detection~\citep{benosman_asynchronous_2012, dardelet}  (Benosman 2012, Dardelet 2021).

\subsection{Main limits}

@@

\subsection{Perspectives}

%Note that this supervised learning scheme can be extended to a variety of tasks. It would follow from the emergence of new kernels adapted to this new task after supervised learning.  This constitutes a major advantage over other algorithms which derive event-based algorithms from specific physical rules (see for instance~\citep{benosman_asynchronous_2012} for computing the optic flow using the luminance conservation rule). We aim at extending the application of this model on more generic datasets acquired in natural conditions for progressively more complex tasks from motion extraction, optic flow or time-to-contact maps.
%
